$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-02 paper/paper.tex
Fix silly mistakes -- thanks Erika!

\subsection{Contributions}
Our contributions are the following:
\begin{itemize}
\item \textbf{Formalisation of the syntax and the semantics of the \picalc{}}:
  \autoref{syntax} uses type level de Bruijn indices \cite{deBruijn1972} to introduce a syntax that is well-scoped by construction: every free variable is accounted for in the type of the process that uses it.
  \autoref{semantics} provides an operational semantics for the untyped \picalc{}, prior to any typing.
  This operational semantics is given as a reduction relation on processes.
  The reduction relation tracks at the type level what channel the communication occurs on, so that this information can then be used to state subject reduction --- ak-a type preservation.
  It is also defined modulo structural congruence --- a relation that acts as a quotient type that gets rid of the unecessary syntactic minutiae introduced by the syntax of the \picalc{}.

@@

  \inferrule
  { }
  {\constr{comp-assoc} : \comp{P}{\comp{Q}{R}} \eqeq \comp{\comp{P}{Q}}{R}}

@@

The first three rules ($\constr{comp}-$*) state associativity, symmetry, and $\PO$ as the neutral element of parallel composition, respectively.
The last three ($\constr{scope}-$*) state, garbage collection, scope extrusion and commutativity of restrictions, respectively.

>>>>

\subsection{Contributions}
Our contributions are the following:
\begin{itemize}
\item \textbf{Formalisation of the syntax and the semantics of the \picalc{}}:
  \autoref{syntax} uses type level de Bruijn indices \cite{deBruijn1972} to introduce a syntax that is well-scoped by construction: every free variable is accounted for in the type of the process that uses it.
  \autoref{semantics} provides an operational semantics for the untyped \picalc{}, prior to any typing.
  This operational semantics is given as a reduction relation on processes.
  The reduction relation tracks at the type level what channel the communication occurs on, so that this information can then be used to state subject reduction --- aka type preservation.
  It is also defined modulo structural congruence --- a relation that acts as a quotient type that gets rid of the unecessary syntactic minutiae introduced by the syntax of the \picalc{}.

@@

  \inferrule
  { }
  {\constr{comp-assoc} : \comp{P}{(\comp{Q}{R})} \eqeq \comp{(\comp{P}{Q})}{R}}

@@

The first three rules ($\constr{comp}-$*) state associativity, symmetry, and $\PO$ as the neutral element of parallel composition, respectively.
The last three ($\constr{scope}-$*) state garbage collection, scope extrusion and commutativity of restrictions, respectively.
